\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore, sweep efficiency may reduce further or early breakthrough may result \citep{riaz_2004, tavassoli_2015}. During immiscible $CO_{2}$ flooding, $CO_{2}$ turns into supercritical phase under under high pressure and temperature. The density of supercritical $CO_{2}$ is usually lower than the \textit{in-situ} hydrocarbons therefore it may override oil. The viscocity of supercritical $CO_{2}$ is much smaller than that of the oil thus viscous fingering and/or channeling may result. The outcome of the above operations \textit{viscous fingering}.

>>>>

\medskip
Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore sweep efficiency may be reduced or early breakthrough may occur \citep{riaz_2004, tavassoli_2015}. During immiscible CO$_{2}$ flooding, density of supercritical CO$_{2}$ is usually lower than the \textit{in-situ} hydrocarbons, \red{therefore it may override oil (?)}. Viscosity of supercritical CO$_{2}$ is also significantly smaller than that of the oil thus viscous fingering and/or channelling may occur. The outcome of the above operations \textit{viscous fingering} \red{(Merge these 2 sentences ... remember sentences often need to be long than a single line and shorter than 3-4 lines!!)}.
